### 2020-05-26 case-studies.tex
first draft of livelit expansion section

\subsubsection{Livelit Expansion} abc

\subsubsection{Typed Hygienic Splicing} abc

>>>>

\subsubsection{Livelit Expansion} 
Livelit expressions are given dynamic meaning by expansion to standard expressions, i.e. expressions without livelits.
The expansion of Fig.~\ref{fig:grading} is:\todo{change code once figure is final}{}

\begin{lstlisting}
let grades = (
  ["A1", "A2", "A3", "A4", "Midterm", "Final"],
  ("Cyrus", [0.0, 0.0, 0.0, 0.0, 0.0]),
  ("Nick", [0.0, 0.0, 0.0, 0.0, 0.0]),
  ("David", [0.0, 0.0, 0.0, 0.0, 0.0])) in 
let averages = compute_averages(grades) in 
let cutoffs = (.A 90.0, .B 80.0, .C 70.0, .D 60.0) in 
format_for_university(assign_grades(averages, cutoffs))
\end{lstlisting}

The programmer can request to see this expansion in Hazel. 
Ideally, however, it would not be necessary to inspect the underlying expansion 
(or the livelit implementation, discussed in Sec.~\ref{sec:livelit-definitions}) 
to reason about types and binding. 
After all, one does not need to look inside 
function bodies to reason about types and binding.
Instead, in the words of Reynolds\todo{cite}{}, 
``type structure is a syntactic discipline for maintaining levels of abstraction''.
The livelits mechanism supports reasoning abstractly about types and binding by 
several means.

First, to support abstract reasoning about the type of the expansion, 
livelit definitions must specify an \emph{expansion type} in their declarations.
The declarations of the two livelits in Fig.~\ref{fig:grading}, 
eliding their implementations for now, are:
\begin{lstlisting}[numbers=none]
livelit $dataframe at Dataframe { ... }
livelit $cutoffs(averages: List(Float)) 
  at (.A Float, .B Float, .C Float, .D Float) { ... }
\end{lstlisting}
The expansion type of \li{\$dataframe} is \li{Dataframe} 
(a type for tabular floating point data together with string row and column keys, consistent with the expression in the expansion above)
and the expansion type of \li{\$cutoffs} is a labeled product of grade cutoffs (Hazel notates labels \li{.label}).

\subsubsection{Typed Hygienic Splicing and Parameterization} abc

unlike arguments, not a fixed number of splices (e.g. adding a new row or column by pressing those buttons)

### 2020-05-26 livelits-paper.tex
first draft of livelit expansion section

\usepackage{listings}%
\lstloadlanguages{ML}
\lstset{tabsize=2, 
basicstyle=\footnotesize\ttfamily, 
% keywordstyle=\sffamily,
commentstyle=\itshape\ttfamily\color{gray}, 
stringstyle=\ttfamily\color{purple},
mathescape=false,escapechar=\#,
numbers=left, numberstyle=\scriptsize\color{gray}\ttfamily, language=ML, showspaces=false,showstringspaces=false,xleftmargin=15pt, 
morekeywords={string, float, int, Int, Float, String, livelit},
classoffset=0,belowskip=\smallskipamount, aboveskip=\smallskipamount,
moredelim=**[is][\color{red}]{SSTR}{ESTR}
}
\newcommand{\li}[1]{\lstinline[basicstyle=\ttfamily\fontsize{9pt}{1em}\selectfont]{#1}}
\newcommand{\lismall}[1]{\lstinline[basicstyle=\ttfamily\fontsize{9pt}{1em}\selectfont]{#1}}

>>>>

\usepackage{listings}%
\lstloadlanguages{ML}
\lstset{tabsize=2, 
basicstyle=\footnotesize\ttfamily, 
% keywordstyle=\sffamily,
commentstyle=\itshape\ttfamily\color{gray}, 
stringstyle=\ttfamily\color{purple},
mathescape=false,escapechar=\#,
numbers=left, numberstyle=\scriptsize\color{gray}\ttfamily, language=ML, showspaces=false,showstringspaces=false,xleftmargin=15pt, 
morekeywords={string, float, int, Int, Float, String, livelit, at, List},
classoffset=0,belowskip=\smallskipamount, aboveskip=\smallskipamount,
moredelim=**[is][\color{red}]{SSTR}{ESTR}
}
\newcommand{\li}[1]{\lstinline[basicstyle=\ttfamily\fontsize{9pt}{1em}\selectfont]{#1}}
\newcommand{\lismall}[1]{\lstinline[basicstyle=\ttfamily\fontsize{9pt}{1em}\selectfont]{#1}}
